### 2025-03-25 notes/ms.tex
update

\subsection{Definition}

@@

>>>>

\subsection{Minimizing area of regular surfaces in \(\mathbb{R}^3\)}

@@

\begin{thing6}{Extra, we discussed this at some time}\leavevmode
That \textit{\textbf{hypersurface}} is a thing locally defined by \textit{one} function.
\end{thing6}

\section{Class 3}

\subsection{Isothermic coordinates}

A \textit{\textbf{Weyl transformation}} is a map of metrics
\[g \mapsto  e^kg\]
where we use exponent just to mean an invertible positive number. \(k\) is a real function.

\begin{upshot}\leavevmode
That a metric on a surface induces a complex structure given by anticlockwise 90-degree rotation. And the interesting part is that two conformal metrics induce the same conformal structure, and the map that relates these metric is the Weyl transform.
\end{upshot}

\begin{thing8}{Example: euclidean coordinates}\leavevmode
Euclidean metric is \((du)^2+(dv)^2\). Letting \(dz:=du+idv\) and \(d\bar{z}:=du-i dv\) we get
\[(du)^2+(dv)^2=(dz)\cdot(d\bar{z})\]
Now take other coordinates \(w\), \(w=F(z)\).  You'll get
\[dw\cdot d \bar{w}=\underbrace{|F^i(z)|^2}_{e^k}dz\cdot d\bar{z}=e^k((du)^2+(dv)^2)\]
And the matrix is
\[\begin{pmatrix}e^k&0\\ 0&e^k\end{pmatrix}\]

\textbf{Conclusion:} conformal class of metric is the same as complex structure.
\end{thing8}

\begin{defn}\leavevmode
\textit{\textbf{Isothermic coordinates}} are local coordinates \((u,v)\) such that \(g_{11}=g_{22}\) and \(g_{12}=0\). So,  \textbf{scalar} multiple of euclidean metric.
\end{defn}

\begin{claim}\leavevmode
Any Riemannian surface \((\Sigma,g)\) has local isothermic coordinates. (In fact, for every power series we get another isothermic coordinates. There is a group action of the \textit{\textbf{local biholomorphisms}}. In higher dimension this is only finite dimensional, generated by inversions (this is a group, like inversion about circle in \(\mathbb{C}\) and isometries (i.e. \(\operatorname{Isom}(\mathbb{R}^n) \supset\mathsf{O}(n),\mathbb{R}^n\)). So conclusion: in dimension 2 it has to do with complex analysis and in higher dimension it's just different.)
\end{claim}

\begin{thing7}{We have learnt}\leavevmode
that there are some thing of complex analysis like maximum principle and probably also Schwarz principle that generalize to higher dimension, but not everything.
\end{thing7}

\begin{remark}\leavevmode
Recall that conformal maps are either holomorphic or antiholomorphic.
\end{remark}

\subsection{Grassmanian}

Recall what is grassmanian \(\operatorname{Gr}(m,n)\) with \(m<n\), the variety of \(m\)-dimensional vector subspaces of an \(n\)-dimensional vector space \(V\), and Plucker embedding \(\operatorname{Gr}(m,n)\hookrightarrow \mathbb{P}\Lambda^{m}V\).

\begin{defn}\leavevmode
\(V\) has \textit{\textbf{vectors}}. \(V^\vee\) has \textit{\textbf{covectors}}.  \(\Lambda^{2}V\) has \textit{\textbf{bivectors}}.  \(\Lambda^{3}V\) \textit{\textbf{trivectors}}.  \textit{\textbf{Polyvectors}}. For bundles:  \(\Lambda^{2}T_M\) \textit{\textbf{bivector fields}}.  \(\Lambda^{m}T_M\) \textit{\textbf{polyvector (or multivector) fields}}, they are dual to  \(\Omega^{m}=\Lambda^{m}\Omega\), differential \(m\)-forms.
\end{defn}
For a subspace \(U \subset V\) we get corresponding \(\underbrace{\Lambda^{m}U }_{\substack{\text{1-dim casr}  \\ \cong\mathbb{R}}}\xrightarrow{\Lambda^{m}j}\Lambda^{m}V\)
and corresponidingly
\[\underbrace{\mathbb{P}\Lambda^{m}U}_{\substack{\text{1 dim}  \\ =pt}}\xrightarrow{\mathbb{P}(\Lambda^{m}j)}\mathbb{P}\Lambda^{m}U\]

Next. If \(V=\mathbb{R}^n\) is equipped with a metric \(g\) you have for two orthonormal bases
\[e_1 \wedge \ldots \wedge e_m=\det C f_1\wedge \ldots \wedge f_m\]
For a map \(f_i=C_i^j e_j\). If they are orthonormal you get \(\det C=\pm 1\) and of you orient it all you get \(\det C=1\).

Correspondingly define the space of \textit{oriented} vector subspaces of euclidean space by \(\operatorname{Gr}^+(m,\mathbb{R}^n)\).
For a basis \(U=\left<u_1,\ldots,u_m\right>\), we get a basis \(\Lambda^{m}U=\left<u_1\wedge u_2\wedge\ldots \wedge u_m\right>\).

\begin{example}\leavevmode
\begin{itemize}
\item \(\operatorname{Gr}(1,2)=\) circle.
\item \(\operatorname{Gr}^+(1,2)\) space of rays.
\item \(\operatorname{Gr}^+(1,\mathbb{R}^n)=S^{n-1}\).
\item \(\operatorname{Gr}(1,\mathbb{R}^n)=\mathbb{R}P^{n-1}\).
\end{itemize}
\end{example}

Now do
\[\begin{tikzcd}0\arrow[r]&U^{(m)}\arrow[r]&V^{(n)}\arrow[r]&Q^{(n-m)}\arrow[r]&0\end{tikzcd}\]
dualize
\[\begin{tikzcd}0\arrow[r]&Q^\vee\arrow[r]&V^\vee\arrow[r]&U^\vee\arrow[r]&0\end{tikzcd}\]
So you automatically get isomorfphism
\[\operatorname{Gr}(m,V)=\operatorname{Gr}(V,n-m)=\operatorname{Gr}(n-m,V^\vee)=\operatorname{Gr}(V^\vee,m)\]
And now pick some orientation on \(V\), you shall get 
\begin{exercise}\leavevmode
\(\Lambda^{n}V \cong \Lambda^{m}U \otimes \Lambda^{n-m}Q\)
\end{exercise}

\begin{example}\leavevmode
\(\operatorname{Gr}^+(2,3)=S^2=\) conic \(\subset\mathbb{C}P^{2}\), more exactly \(\{x^2+y^2+z^2=0\}\).
\end{example}

\begin{exercise}\leavevmode
\(\operatorname{Gr}^+(2,\mathbb{R}^n)\cong Q^{n-2}\subset \mathbb{C}P^{n-1}\) of the form \(\left\{\sum_{i=1}^n z_i^2=0\right\}\)
\end{exercise}

\subsection{ Now}
Consider 
\[M^{(m)}\xrightarrow{f}N^{(2)}\]
and do
\[\mathbb{R}^m \cong T_p^m M \xrightarrow{d_pf}T_{f(p)}N \cong \mathbb{R}^n\]
so for every regular (=rank is \(m\)=the map is an embedding=the thing is a subvariety) \(p\) you get a point in grassmanian
\[\operatorname{Gr}(m,T_{f(p)}N)\]
Consider \(f^*T_N\) which is a vector bundle over \(M\), then we can consider
\[(df):T^{(m)}_M \overset{\text{by regularity,} }{\hookrightarrow } f^*T^{(n)}_N \to \underbrace{f^*(T_N / df(T_M))^{n-m}}_{\text{\textit{\textbf{normal bundle}}} }\]
and then consider the \textit{\textbf{Grassmanization}} of \(f^*T_N\), which is a bundle
\[\begin{tikzcd}
\operatorname{Gr}(m,f^*T_N)\arrow[d]\\
M
\end{tikzcd}\]
Now consider sections of this thing.

\begin{thing7}{Important observation}\leavevmode
 Given a trivialization of \(f^*T_N\), a section of the thing becomes just a map
 \[M \to \operatorname{Gr}(m,n)\]
 (Because a section of a trivial bundle is just a map to the fiber.) 
\end{thing7}

Now fix \(N:= \mathbb{R}^n\) and put a connection, the Levi-Civita connection. Actually now better take the oriented Grassmanian for the whole bussiness. And we have the map
\[M \to \operatorname{Gr}^+(m,n)\]
which is a map that to every point associates its tangent space. And it is called the \textit{\textbf{Gauss map}}.

Recall that
\begin{claim}\leavevmode
A surface is minimal \(\iff\) Gauss map is conformal (anti-holomorphic).
\end{claim}

Put a surface in \(\mathbb{R}^3\). Basis for tangent space is
\[(x_u,y_u,z_u), (x_v,y_v,z_v)\]
So basis for projectivization is
\[(y_uz_u-y_vz_u, x_uz_v-x_vz_u,x_uy_v,x_vy_u)\]
and in general, when you get
\begin{align*}
\Sigma&\to \mathbb{R}^n\\
\frac{\partial }{\partial u}x, \frac{\partial }{\partial v}X &\rightsquigarrow \frac{\partial x}{\partial u}\wedge \frac{\partial x}{\partial v}
\end{align*}
\begin{thing8}{Lesson}\leavevmode
Plücker coordinates of oriented Grassmanian are the same as coordinates of normal bundle!
\end{thing8}
But also notice that you can write
\[\{x^i,x^j\}_{du \wedge dv}\]
And the point of all this is that

\begin{claim}\leavevmode
Minimal surfaces are equivalently defined as the ciritical points of the \textit{\textbf{Schild action}} 
\[\int \left(\sum_{i<j}\{x_i,x_j\}^2\right)\omega\]

\end{claim}
Now put a curve \(I \subset \Sigma \to \mathbb{R}^n\)… [what was the curve for…?]

\begin{thing7}{Hint}\leavevmode
From 1 to 2 you ``vary" the volume and look for critical points.
\end{thing7}

\begin{thing6}{Important exercise}\leavevmode
If \(x=u,y=v\) and \(z=\varphi(u,v)\), you get two derivatives
\[\partial_u \to (1,0,\varphi_u)\qquad \partial_v \to (0,1,\varphi_v)\]
Notice that
\[df[\partial_u]=\partial_x+\varphi_u\cdot \partial_z\]
And now
\[\partial_u \wedge \partial_v = \partial_u \wedge \partial_y- \varphi_v\partial_x \wedge\partial_z-\varphi_v \partial_y \wedge \partial_z\]
Then you have proportionality
\[N \sim (-\varphi_u,-\varphi_v,1):=\tilde{N}\]
So
\[\|\tilde{N}\|^2=\varphi_u^2+\varphi_v^2+1=g\]
\[N=\frac{\tilde{N}}{\sqrt{g} }\]
So \textit{\textbf{Gauss map for non-parametric surface}} is 
\[G:(u,v) \longrightarrow\left(\frac{-\varphi_u}{\sqrt{1+\varphi^2_u+\varphi^2_v} },\frac{-\varphi_v}{\sqrt{1-\varphi^2_u+\varphi^2_v} },\frac{1}{\sqrt{1-\varphi_u^2+\varphi_v^2} }\right) \]
(and you can just write \(\sqrt{1+\varphi_u^2+\varphi_v^2} =\sqrt{g} \) but Ok). Similarly…
\end{thing6}

And differentiate!
\[dG:T_pM \to T_{G(p)}\operatorname{Gr}(m,n)=\operatorname{Hom}(T_pM,\text{Normal bandle}N )\]
So you see
\[dG \in \operatorname{Hom}(T_pM,\operatorname{Hom}(T_pM, N))\]
So it's a map
\(T_pM \times T_pM \to N\) 
But \(N\) is trivialized! So you can think of  \textit{numbers}. So it's a form.

\begin{claim}\leavevmode
That map is symmetric.
\end{claim}
So you can define it to be the \textit{\textbf{second fundamental form}}.

\begin{thing8}{Notations}\leavevmode
\begin{itemize}
\item I fundamental form \(\rightsquigarrow \) \(g_{ij}\).
\item  II fundamental form \(\rightsquigarrow \) \(B_{ij}\) for a vector in the normal bundle, and \(b_{ij}\) when you are in \(\mathbb{R}^3\) and you have trivialized it to get numbers
\end{itemize}
\end{thing8}

\begin{claim}\leavevmode
\[B_{ij}=\left(\frac{\partial^2 \vec{x}}{\partial u_i\partial u_j}\right)^N \]
where exponent \(N\) means projection to the normal bundle which can mean algebraic projection when you think of a quotient bundle or orthogonal projection when you think geometric.
\end{claim}

\begin{thing6}{Reminder of the end of last lecture}[Variation of the tangent direction]\leavevmode
	\begin{align*}V'(t=0)[\underbrace{\delta \varphi}_{:=w}]= \int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv\\
		&=\int \left<\delta \varphi,\text{something} \right>\frac{\sqrt{g} dudv}{\text{volume form} }
	\end{align*}
where \(\delta \varphi\) is a section of \(f^* T_{\mathbb{R}^n}=df(T_M) \oplus^\perp N\). And \textbf{something} is a unique thing that exists making the equality hold. This is a possible definition of \textit{\textbf{mean curvature vector}} \(\vec{H} \in N\).

And you can also write
\[\int dv \wedge \left(\frac{z_u}{\sqrt{g} \cdot w_u du}\right) = \int dv \wedge \left(\frac{z_u}{\sqrt{g} }dw\right) \]
where \(dw=w_u du+\ldots+dv\). And now we want to integrate by parts so if you recall
\[=-\int w \cdot \partia\left(\frac{z_u}{v_g}dv\right) \]
So the integral above becomes
\begin{align*}
\int_{\Sigma}\frac{z_x\cdot w_x+z_y\cdot w_y}{\sqrt{g} }dudv&=-\int \left(\partial_u \left(\frac{z_u}{\sqrt{g} }\right)+\left(\partial_v \frac{z_v}{\sqrt{g} } \right) \cdot w du dv
\end{align*}
so if that is zero for all \(w\).
\end{thing6}

Right so that is the \textit{\textbf{first variation of volume}}? It's
\[V'|_{t=0}=-\int_\Sigma(\sqrt{g} du) \left<H,W\right>\]
And it has all to do with the expression \(\Sigma g^{ij}B_{ij}\).
